Benchmarking Python Deep Learning Frameworks\\ for Language Modeling on GPUs

### 2016-12-14 paper/main.tex
updating 2.2 frameworks section

\subsection{Frameworks}
All three frameworks use a symbolic computation graph, which maps operations and variables to nodes in a graph. To perform computation, one has to ``query'' the graph, providing values for variables needed to compute the desired output.
Figure~\ref{fig:compGraph}\footnote{Taken from \cite{tensorflow}} shows an example of a simple computation graph. All three frameworks efficiently handle queries, by only computing nodes that are necessary for the output requested.\ms{Can we confirm that's true?}

\begin{figure}\begin{center}
\includegraphics[scale=.4]{graphics/tensorflowGraph.png}
\caption{\label{fig:compGraph}Simple neural computation graph example. \texttt{ReLU} is a rectified linear unit.} 
\end{center}\end{figure}

All our frameworks run a \texttt{Python} wrapper\ms{TODO: add footnote about which version of Python}, with a \texttt{C++} backend. Both TensorFlow and DyNet make extensive use of the Eigen library for C++, which provides fast low-level linear algebra for matrix and tensor operations. Theano's backend uses the BLAS linear algebra libraries instead.
\ms{TODO: more spiel? E.g. static computation graph (theano, tf) vs dynamic (Dynet)}
%TensorFlow's computation graph is pure \texttt{Python}, which makes it slower than other frameworks.

>>>>

\subsection{Frameworks}
All three frameworks use a symbolic computation graph, which maps operations and variables to nodes in a graph. To perform a computation, one has to ``query'' the graph by providing values for variables needed to compute the desired output.
Figure~\ref{fig:compGraph} shows an example of a simple computation graph.

\begin{figure}\begin{center}
\includegraphics[scale=.4]{graphics/tensorflowGraph.png}
\caption{\label{fig:compGraph}Simple neural computation graph example. (\texttt{ReLU} is a rectified linear unit.) Figure is taken from \protect\cite{tensorflow}.} 
\end{center}\end{figure}

The frameworks handle computation graphs differently. Theano and Tensorflow perform ``static'' declaration of computation graphs: first, the graph architecture is specified, and then data is run through the compiled graph to train or make predictions. In contrast, DyNet does ``dynamic'' declaration of computation graphs; that is, the computation graph is defined on-the-fly as operations are executed.

All of the frameworks we tested have Python APIs\footnote{DyNet was originally a C++ framework which now has a Python wrapper; currently its Python wrapper only supports Python 2. TensorFlow and Theano are primarily Python frameworks that support both Python 2 and 3.} that wrap C++ or optimized Python code (e.g., numpy).

For speed, the frameworks all use fast low-level linear algebra libraries for matrix and tensor operations. Both TensorFlow and DyNet make extensive use of the Eigen library for C++, while Theano uses BLAS instead.

%TensorFlow's computation graph is pure \texttt{Python}, which makes it slower than other frameworks.
